Innovations Report: Procedural Fur System

### 2018-03-18 docs/paper.tex
added appendix

Whilst rendering and shading triangulated meshes is relatively straightforward, as described in \cite{objLoading}, there are multiple different approaches one could use to render curves. The technique I chose to implement relies on drawing an empty VAO multiple times, and using \texttt{gl\_PrimitiveIDIn} from within a geometry shader to determine which curve from the bound \texttt{GL\_SHADER\_STORAGE\_BUFFER} should be drawn. Figure~\ref\{} shows how this was achieved.

@@

>>>>

Whilst rendering and shading triangulated meshes is relatively straightforward, as described in \cite{objLoading}, there are multiple different approaches one could use to render curves. The technique I chose to implement relies on drawing an empty VAO multiple times, and using \texttt{gl\_PrimitiveIDIn} from within a geometry shader to determine which curve from the bound \texttt{GL\_SHADER\_STORAGE\_BUFFER} should be drawn. Listings~\ref{lst:rendercpp} and ~\ref{lst:renderglsl} shows how this was achieved.

@@

\newpage
\appendix

\begin{lstlisting}[language=C++, label={lst:rendercpp}, caption={Extract from the C++ application code showing how Curves are rendered procedurally. \texttt{emptyVAO} is an empty Vertex Array Object, \texttt{curvesSSBO} is a \texttt{GL\_SHADER\_STORAGE\_BUFFER} containing vertex data for multiple curves, and \texttt{indices} is the number of curves in the buffer.}]
glBindVertexArray(emptyVAO);
glBindBufferBase(GL_SHADER_STORAGE_BUFFER, 0, curvesSSBO);
glDrawArrays(GL_POINTS, 0, indices);
\end{lstlisting}

\begin{lstlisting}[language=GLSL, label={lst:renderglsl}, caption={Extract from the curves rendering geometry shader, showing how vertex positions were processed from data stored in a bound \texttt{GL\_SHADER\_STORAGE\_BUFFER}.}]
#version 430 core
layout(points) in;
layout(line_strip, max_vertices = 5) out;

layout (std430, binding = 0) buffer curvesBuffer
{
	Curve curves[];
};

uniform mat4 MVP;

void main()
{
	for (int i = 0; i < 5; ++i)
	{
		gl_Position = MVP * vec4(curves[gl_PrimitiveIDIn].position[i].xyz, 1.0);
		EmitVertex();
	}
	EndPrimitive();
}
\end{lstlisting}
